\documentclass[a4paper,colorinlistoftodos]{article}
\input{preamble}
\input{hide}

\author{Upal Bhattacharya}
\date{\today}
\title{Structured Prompt Interrogation and Recursive Extraction of Semantics (SPIRES): a method for populating knowledge bases using zero-shot learning}
\begin{document}

\maketitle

\begingroup
    \hypersetup{linkcolor=black}
    \tableofcontents
    \pagebreak
\endgroup

\linenumbers


\section{Reading TODOs}

\begin{itemize}
  \item[\faCheckSquareO] Abstract
  \item[\faCheckSquareO] Introduction
  \item[\faCheckSquareO] Conclusion
  \item[\faSquareO] Results
  \item[\faSquareO] Methods
  \item[\faSquareO] Summary
  \item[\faSquareO] Verdict
\end{itemize}

\section{Abstract + Introduction + Conclusion}
\begin{caution}{}{caution-1}
Uses Knowledge Base and ontology interchangeably. This can create
implementation confusion.
\end{caution}

\begin{itemize}
  \item Performs zero-shot recursive prompting to align LLM responses with a
    user-defined schema and an input text
    \begin{query}{}{query-1}
      Is the user-defined schema part of the prompt input or the gold standard
      against which the output is evaluated?
    \end{query}
  \item Uses existing ontologies and vocabularies to substantiate matched
    elements with identifiers
  \item Can perform new tasks without new training data
  \item \hlgreen{NLP methods can assist KB construction at several stages:
      automatic selection of relevant data,NER for entity/term/concept
      identification, RE for taxonomic and non-hierarchical relation
      extraction}
  \item Schemas define structure but complex schemas are difficult to
    populate 
  \item \hlgreen{SPIRES performs automatic population of custom schemas and
    ontology models}
\end{itemize}

\section{Methods}

\begin{itemize}
  \item A schema is a collection of classes/concepts which can be instantiated
    with instances. Each class has a list of attributes.
    \begin{query}{}{query-2}
      What is the exact form of these attributes?
    \end{query}
    An attribute has associated properties which include its name, range, etc.
   \item Models are prompted with terms from 4 ontologies with a request to
     retrieve the identifiers from the ontology.
     \begin{query}{}{query-3}
       Are identifiers like IDs e.g. GO ID? Does that not make this the same
       task as in \cite{bombieri2025DoLlmsDream}? 

    \end{query}
 
 
\end{itemize}

\section{Results}

\section{Summary}

\section{Verdict}



% \bibliographystyle{splncs04nat}
% \bibliography{/home/upal/References/bibliography.bib}
\printbibliography

\pagebreak
\nolinenumbers
\appendix

\begingroup
    \hypersetup{linkcolor=black}
    \listoftodos
    \listofchanges
    \pagebreak
\endgroup

\printbibliography
\end{document}

